% -*- latex -*-
\documentclass{tccontract}
\def\date{July 1, 2002}
\begin{document}

\begin{header}{Software License Agreement}
\stdhead{Destination Imagination, Inc, of Glassboro, New Jersey}{\date{}}
\end{header}

\begin{body}

%====================================================================
\clause{Representation of Client and Consultant}
%====================================================================

Client and Consultant agree that the representatives named herein as
signatories to this document are fully empowered, authorized, and
solely responsible for all decisions referenced in this document
requiring mutual agreement between Client and Consultant.  Mutual
agreement may be documented in writing, by fax, or by E-mail.

%====================================================================
\clause{The Agreement}
%====================================================================

This license agreement (the ``Agreement'') covers the use of both
existing and new software, related information and documentation
developed by the Consultant and supplied to the Client to assist with
the web-based capture and processing of membership and team
information (the ``System''). The use of this software by the Client
constitutes agreement to be bound by the terms of this license.


This Agreement supersedes and replaces all previous licenses in
respect of the System, and constitutes the entire agreement between
the parties with respect to its subject matter, and supersedes all
prior agreements, understandings, proposals, representations and
discussions between the parties, whether oral or written. There are no
understandings, agreements, representations or warranties, expressed
or implied not expressly specified herein.

This Agreement cannot be changed except by written agreement between
the parties.

%====================================================================
\clause{Working Relationship}
%====================================================================

The Software described herein will be developed according to the
proposal previously delivered to the Client and the following
guidelines, which may be modified from time to time and at any time by
mutual agreement.

Consultant shall begin to construct the Software immediately upon
execution of this Agreement. The Consultant will report progress on
demand to the Client. The Consultant will make a best-efforts attempt
to deliver sufficient functionality of the System by September 1st to
allow Destination Imagination to capture and process membership
registrations. Thereafter Consultant agrees to deliver the remaining
functionality as quickly as possible.

For the duration of the Agreement, Consultant will provide Client with
support. Such support is limited to investigating and repairing
defects in the System. This support does not include the provision of
new functionality in the System.

Client agrees that certain defects may be attributable to third
parties outside the Consultant's control.  Consultant agrees to use
its best efforts to provide work-arounds or alternate products to
remedy said defects where possible.

%====================================================================
\clause{Payment Terms}
%====================================================================

Consultant will invoice client according to the provisions of Schedule
A. Client agrees to pay these invoices within 30 days of receipt.

%===================================================================
\clause{Ownership and Grant of license}
%===================================================================

The Consultant grants the client a non-exclusive, worldwide, limited
right to

\begin{enumerate}
\item install and operate the source code of the System on Client
      computer
      systems; and
\item make reasonable numbers of back-up copies of the System
      software.
\end{enumerate}

This license does not permit the Client to redistribute or relicense
the System, nor to modify the source code of the System.  The Client
may not transfer any rights or obligations under this Agreement to any
other person or organization except as part of a bona-fide
restructuring of the Client's business.

%====================================================================
\clause{Term and Termination}
%====================================================================

Upon payment of the license fee, this license grants the Client the
right to use the System for a period of one year from the date of this
Agreement. Thereafter this license may be renewed each year on payment
of the then-appropriate license fee. The Consultant may not
unreasonably refuse to renew the Agreement. Should the Consultant
refuse without cause or be unable to renew the Agreement the Client
shall be granted a perpetual license to continue to use the software
as described in this Agreement and to make enhancements to the source
code of the System. In these circumstances any other obligations of
the Consultant under this agreement will be terminated.

Failure by the Client to comply with the terms of this Agreement
constitute reason to terminate the Agreement and constitute cause not
to grant future licenses.


%====================================================================
\clause{Intellectual Property Rights}
%====================================================================

The System is protected by international copyright laws and treaty
provisions, as well as other intellectual property laws and
treaties. The System is licensed, not sold.  All rights not
specifically granted under this Agreement are reserved by the
Consultant.

%====================================================================
\clause{Provision of Services}
%====================================================================

Consultant shall not sub-contract services to any third-party  
or add any additional staff to provide services unless agreed to in
writing by Client.

%====================================================================
\clause{Indemnification}
%====================================================================

\begin{enumerate}
\item Consultant shall defend (or at its option settle), indemnify,
  and hold Client and its officers, directors, employees, agents,
  successors, and assigns (collectively, Client Indemnitees) harmless
  from and against any claim arising out of bodily injury (including
  death) or damage to property that occurs in connection with the
  performance by Consultant of its obligations under this Agreement,
  to the extent that such injury or damage is caused by the acts,
  errors, omissions, or negligence of Consultant's employees or
  agents, and from and against any and all liabilities, losses, costs,
  damages, penalties and expenses (including reasonable attorneys'
  fees) associated with such claim or action incurred by any Client
  Indemnitee.
  
\item Consultant shall defend, (or, at its option, settle) indemnify,
  and hold Client Indemnitees harmless from and against any claim
  brought by any third party against any of them for actual or alleged
  infringement of any patent, trademark, copyright, or similar
  property right (including, but not limited to, misappropriation of
  trade secrets) to the extent based upon the System developed under
  this agreement, and from and against any and all liabilities,
  losses, costs, damages, and expenses (including reasonable
  attorneys' fees) associated with any such claim or action incurred
  by any Client Indemnitee.
  
\item Client agrees to give Consultant: (i) prompt written notice of
  any claim requiring Consultant indemnification under this Contract;
  (ii) complete authority to defend or, at Consultant's option, settle
  any such claim; and (iii) reasonable assistance and cooperation in
  connection with such claim.
\end{enumerate}

%====================================================================
\clause{Arbitration}
%====================================================================

The parties will endeavor in good faith to resolve any and all
disputes arising under this Agreement by good faith negotiations, with
escalation to the chief executive officer of each company for
resolution as necessary.  

If not resolved by such negotiations within thirty (30) days after
either party has given written notice of the dispute to the other
party, the parties agree to submit the dispute to a third-party
mediator for a non-binding mediation pursuant to the commercial
mediation rules of the American Arbitration Association.  

Any dispute not otherwise settled in accordance with the above
procedures arising out of or relating to this Agreement, including any
issues relating to arbitrability or the scope of this arbitrability
clause, will be finally settled by binding arbitration in accordance
with the commercial rules of the American Arbitration Association.
Judgment upon the award rendered by the arbitrators may be entered by
any court of competent jurisdiction. 

The arbitration will be held in the Dallas, Texas metropolitan area.

Notwithstanding the foregoing, either party may bring a claim for
injunctive relief for breach of confidentiality or license limitation
provisions of this Agreement in any court of competent jurisdiction
without first submitting the claim to arbitration.


\clause{Warranty}

Consultant will develop and maintain the System in accordance with
generally and currently accepted consulting principles and
practices. This warranty is in lieu of all other warranties either
expressed or implied.

%====================================================================
\clause{Limitation of Consultant Liability}
%====================================================================
\textsc{ The Consultant's liability to Client for any claim (on
  account of any error, omission, or negligence) for direct damages
  arising out of this agreement, or cost of defense, or expense
  against Consultant, shall not exceed the lesser of \$10,000.00 or
  the total amount of compensation paid by the Client under this
  agreement.}
  
\textsc{The Consultant shall have no liability whatsoever to the Client
for special or consequential damages (including lost profits) of Client.}
  
\textsc{No action, regardless of form, arising out of the transactions under
  this agreement, may be brought by Client more than one year after
  the cause of action has occurred.}

%====================================================================
\clause{Governing Law}
%====================================================================
This Agreement will be governed by and construed in
accordance with the laws of the State of Texas.

%====================================================================
\clause{Force Majeure}
%====================================================================
Neither party shall be liable for delays or failure to deliver or
perform due to causes beyond its reasonable control, acts of God, acts
of the other party, acts of civil or military authorities, fires,
strikes, floods, epidemics, wars, riots, delays in transportation, or
the unavailability of information or material to be furnished by the
other party.

%====================================================================
\clause{All Amendments in Writing}
%====================================================================
This Agreement may not be changed or modified except by a written
agreement, executed on behalf of Consultant and Client.


\end{body}
\sign{Destination Imagination, Inc}{David Thomas}
\end{document}
% LocalWords:  Glassboro Symbian Symbian's licensors Majeure Indemnitees
% LocalWords:  Indemnitee arbitrability
